\documentclass[a4paper,hidelinks,10pt]{article}

\usepackage{titlesec}
\usepackage{titling}
\usepackage[margin=1.5cm]{geometry}
\usepackage{parskip}
\usepackage[hidelinks]{hyperref}
\usepackage{helvet}
\pagenumbering{gobble}
\titleformat{\section}
{\huge\bfseries}
{\hspace{-0.6cm}}
{0em}
{}[\titlerule]

\titleformat{\subsection}[runin]
{\bfseries\large}
{$\bullet$}
{0.4em}
{}[ ---]

\titlespacing{\section}
{0em}{0em}{0.4em}


\titlespacing{\subsection}
{-1em}{0.4em}{1em}

\titlespacing{\subsubsection}
{0em}{0em}{0em}

\titleformat{\subsubsection}
{\bfseries}
{}
{0em}
{}

\begin{document}
\title{R\'esum\'e}
\author{Iurea Marius}
\renewcommand{\maketitle}
{
        \begin{center}
        {\huge\bfseries
        \thetitle

        \theauthor}

        marius.iurea@yahoo.com --- 0741055112

        \end{center}
}

\maketitle

\section{Personal Summary}
A self-motivated individual and passionate student, eager to build products that solve user problems and to take on new challenges.
Team player with good communication skills, adaptable to any work environment.
\section{Technical Skills}
\subsection{Languages}
C, C++, C\#, Python, HTML, JavaScript
\subsection{Frameworks/Libraries}
JQuery, Django
\subsection{Tools}
Git, Unity, Visual Studio, Vim
\section{Projects}
\subsection{RedditFeud}
Webapp build using django, hosted on AWS server \href{https:\\www.redditfeud.com}{(Link)}
\subsubsection{Summary:}
This webapp queries the python reddit API and stores the most popular posts and comments of the past day
in a SQLite database, then when an user requests a quiz it pulls 10 random questions from the database and usesthe template engine to create the webpage.
\subsubsection{Skills Aquired:}

-deployment procces for web app

-understanding of Django and the MVC design pattern

-data scraping using python and the praw API

-JSON file processing

-SQLite

-usage of git for version control

\subsection{Afterswarm}
Game built in Unity for end of highschool project \href{https://mega.nz/#F!e7hGCa6A!YFMBrU9kS6GqHZPJJb20WA}{(Link)}
\subsubsection{Summary:}
This is a small game built in homage to old school "shoot 'em ups". The player is at the bottom of the screen
moving with A and D while aiming with the mouse. There are different enemies with varied shooting styles.

\subsubsection{Skills Aquired:}
-OOP knowledge since Unity is highly object based

-thoroughly reading the documentation

-general game design concepts

-usage of the Unity game engine

\subsection{Bonol}
Implementation of the L game in C++ for a project in university \href{https://github.com/IureaMarius/ProiectIP}{(Link)}
\subsubsection{Summary:}
The L Game is a simple abstract strategy board game. The game was designed to be difficult and skill expresive
game without having many board pieces. The game has a vs CPU mode as well.
\subsubsection{Skills Aquired:}
-further developed problem solving skills and C++ knowledge

-improved at working in a team

-experience creating GUI

-git for version control and cooperation

\section{Education}
\subsection{Currently getting a bachelor's degree at 
the Faculty of Computer Science Iasi(first year student)}
 8.66/10 Grade Average, receiving scholarship 

\subsection{Participation in FIIPractic full-stack .Net courses}
ASP.NET, .NET MVC Core


\end{document}




